### 2016-06-03 thesis_paper/source.tex
thesis

@@

As you can see, speedup bumps up to almost 30 with 10000 atoms (Figure \ref{fg:chart_10000}). Once the overhead on memory transfer is covered by computation speedup, it keeps growing. It is important to pay attention to the growth of speedup over growth of workload. It is not that significant, because even though CPUs are much slower, they still use smart caching and internal multi-core processing, which is pretty fast, too.

@@

>>>>

\vspace{1cm}
\begin{table}[h!]
	\renewcommand*{\arraystretch}{1.5}
	\tabcolsep=0.12cm
  \centering
  \begin{tabular}{| c | c | c | c | c | c |}
   \hline
	Device & Context & Stream & Kernel & Warps Launched & Shared Load \\ \hline
	GRID K520 (0) & 1 & 13 & ${gpu\_one\_body\_function}$ & 32 & 2 \\ \hline
	GRID K520 (0) & 1 & 14 & ${gpu\_two\_body\_function}$ & 32 & 96080 \\ \hline

  \end{tabular}
    \caption{GPU profiling results for 1000 atoms}
    	  \label{tb:gpuprofile1000}
\end{table}

On Table \ref{tb:gpuprofile1000} you can observe results of Nvidia Profiling Tool of how much memory call we did to shared memory for SDH computation. You can also notice that there were 32 warps launched for computing 1000 atoms which is absolutely reasonable, since as we already mentioned one warp (scheduling unit for ultimate parallel execution) has 32 threads maximum, thus ${\frac{1000}{32}}$ \textasciitilde \space$32$. As expected, stream IDs differ for two kernel executions, and both were run on the same GPU device, though we assume that our system can potentially be extended to using multiple GPU devices as well.

@@

As you can see, speedup bumps up to almost 30 with 10000 atoms. Once the overhead on memory transfer is covered by computation speedup, it keeps growing. It is important to pay attention to the growth of speedup over growth of workload. It is not that significant, because even though CPUs are much slower, they still use smart caching and internal multi-core processing, which is pretty fast, too, while GPU does pretty straightforward multicore processing, which is the main reason it stagnates.

@@

When we finally get to the number of atoms that are realistic to the ones scientists use, happily, speedup gets pretty good. Speedup gets up to almost 40 times (Figure \ref{fg:speedup_100000}).
